Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-20 paper-2023-acsos-pulverization.tex
move limitations in the fw and moderate the tone, @metaphori check

\subsection{Limitations of the current version of the DSL}

In its current form, the proposed \ac{dsl} has two major limitations.
%
First and foremost, currently it does not consider openness:
hosts get specified in the runtime and reconfiguration \ac{dsl} as a closed set,
so the specification is not robust to the addition of new hosts or the loss of existing ones.
%
This is a major limitation that,
although planned to be addressed shortly with minor additions to the \ac{dsl},
must be highlighted in this manuscript.
%
The second limitation is related to the policies that can be expressed in the reconfiguration \ac{dsl}:
currently, only policies that can be assessed at the local host level can be assessed.
%
A policy that requires to consider the state of multiple hosts would require to resort to the host language primitive mechanisms and make explicit communications outside the framework,
thus breaking the abstraction.
%
This limitation can be addressed by extending the current reconfiguration
block of the \ac{dsl} in such a way that queries can be performed on any reachable host of the system,
thus making all communications
(including reconfiguration-related ones)
pass through the channels controlled by the framework.

@@

In the future,
we plan to extend the \ac{dsl} to support openness and collective reconfiguration policies.
%
The former will allow devices to join and leave the system at runtime,
while the latter will allow reconfigurations to be performed on the basis of a collective state of the system.
%
Concurrently,
we intend to add support for additional network protocols to be able to support a larger number of practical scenarios.

>>>>

@@

In its current form, the proposed \ac{dsl} has two limitations that will be addressed in the future.
%
First and foremost, it currently does not consider openness,
as hosts get specified in the runtime and reconfiguration \acp{dsl} as a closed set.
%
The second limitation is related to the policies that can be expressed in the reconfiguration \ac{dsl}:
currently, only policies that can be assessed at the local host level can be assessed.
%
A policy that requires to consider the state of multiple hosts would require to resort to the host language primitive mechanisms and make explicit communications outside the framework,
thus breaking the abstraction.
%
This limitation can be addressed by extending the current reconfiguration
block of the \ac{dsl} in such a way that queries can be performed on any reachable host of the system,
thus making all communications
(including reconfiguration-related ones)
pass through the channels controlled by the framework.
%
Concurrently with these extensions,
we intend to add support for additional network protocols to be able to support a larger number of practical scenarios.
